Data Management for LSST Special Programs

### 2024-03-01 sec_intro.tex
Update sec_intro.tex

Data from the Main Survey will be processed with regular (non-special) processing.
This processing will produce, among other data products (LSE-163), 
a contiguous sky footprint that covers at 
least $\sim$18000 deg$^2$ (with $\gtrsim$800 visits per field in WFD regions), 
and is expected to be accomplished with 85--90\% of the observing time.
This contiguous all-sky "deep coadd" may have region-dependent processing parameters and inputs
(e.g., different calibration parameters or deblending algorithms for crowded fields)
and will be of variable depth, as most special regions recieve fewer visits.

\subsection{Regular (non-special) processing}

In some cases, regular processing is also appropriate for Special Programs.

@@

Some science goals for Special Programs can be met with regular processing,
but some will require Special Processing by Rubin Data Management or user-generated processing.

@@

This is a Rubin Data Management term to describe processing that 
uses components of the LSST Science Pipelines and is applied by Rubin
Data Management to images from Special Programs.
Special Processing creates data products that are unique and separate from those produced
by regular processing for the Main Survey.

Special Processing is likely to use different inputs or configurations for the
LSST Science Pipelines, or to run on different timescales, than regular processing - 
as appropriate for the Special Programs' data and science goals.
However, the development and application of specialized \emph{algorithms} or new software
is beyond the scope of Special Processing.

@@

Processing for the DDF images is likely to be a combination of regular (Prompt) processing,
Special Processing, and User-Generated Processing.

@@

Processing for the mini-surveys is likely to be a combination of regular (Prompt) processing,
Special Processing, and User-Generated Processing.

>>>>

Data from the Main Survey will be processed with standard (non-special) processing.
This processing will produce, among other data products (LSE-163), 
a contiguous sky footprint that covers at 
least $\sim$18000 deg$^2$ (with $\gtrsim$800 visits per field in WFD regions), 
and is expected to be accomplished with 85--90\% of the observing time.
This contiguous all-sky "deep coadd" may have region-dependent processing parameters and inputs
(e.g., different calibration parameters or deblending algorithms for crowded fields)
and will be of variable depth, as most special regions recieve fewer visits.

@@

Some science goals for Special Programs can be met with standard processing,
but some will require Special Processing by Rubin Data Management or user-generated processing.

@@

This is a Rubin Data Management term to describe processing that 
uses components of the LSST Science Pipelines and is applied by Rubin
Data Management to images from Special Programs.
Special Processing creates data products that are unique and separate from those produced
by standard processing for the Main Survey.

Special Processing is likely to use different inputs or configurations for the
LSST Science Pipelines, or to run on different timescales, than standard processing - 
as appropriate for the Special Programs' data and science goals.
However, the development and application of specialized \emph{algorithms} or new software
is beyond the scope of Special Processing.

\subsection{Standard (non-special) processing}

In some cases, standard processing is also appropriate for Special Programs.

@@

Processing for the DDF images is likely to be a combination of standard (Prompt) processing,
Special Processing, and User-Generated Processing.

@@

Processing for the mini-surveys is likely to be a combination of standard (Prompt) processing,
Special Processing, and User-Generated Processing.
